Linking Gamification, Ludology and Pedagogy: How to Use Serious Games for Various Knowledge Domains\\

### 2021-10-27 Article/main.tex
Updated Article with Methodology

@@

\subsection{Sampling of Literature}
\subsection{Collection of Case Studies and Determine Similarities}
\subsection{Pinpointing Connected Theories}
\subsection{Extrapolate to other Knowledge Domains}

\section{Findings}
\subsection{Helpful Teaching Theories}
\subsection{Case Studies and the Similarities in Design Principles}

>>>>

One important aspect to note about these knowledge domains is that they are not mutually exclusive as one particular topic can be placed in several of them as the components of that topic may require multiple domains to be properly contained under them.

@@

\subsection{Sampling of Literature}
During this phase key fields of study were identifies for use in working towards the goal of this study. As discussed above, these included the fields of pedagogy (the study of instructional theory), ludology (the study of games with a focus on digital games) and gamification (the use of game-like elements to solve problems). Studying the literature in each of these fields yielded literature that is undoubtedly useful to this study as pedagogy gave insight into instructional theories used in education, ludology provided the necessary understanding of how to study games and the elements that each uses and gamification provided insight into the different knowledge domains and how to best approach each in a teaching environment in addition acting as a bridge for connecting pedagogy to the serious games in ludology. 
\\\\
The bulk of this phase was spent reading articles and identifying which would be useful for this study. It was also during this phase that select case studies were found. These case studies proved useful as each made use of different design principles and as such became another set of literature to be studied.

\subsection{Collection of Case Studies and Determine Similarities}
As case studies were accumulated, only those found that discussed - either directly in great detail or indirectly during the game's description -the design principles followed were selected to be used. Notably, many of those chosen had a focus on some form of digital and cyber security including specific mentions to phishing, social engineering and passwords\cite{Sheng2007, Dincelli2020, snyman2021wolf}. 
\\\\
The following step after finding these case studies was to identify their design principles and determine the major ones that most, if not all, made use of as well as how successful the game was found to be - which is determined in the individual publication either by trails of being judged by experts.

\subsection{Pinpointing Connected Theories}
Once enough literature had been acquired and studied, the connections between each of the fields' theory and case studys' design principles were noted. This was in attempt to identify an overall pattern in the development of serious games for use particularly for educational or training purposes. This included mapping the similarities between the instructional theories to the deign principles of each case study while noting which fields of knowledge the games are a part of.

\subsection{Extrapolate to other Knowledge Domains}
For the knowledge domains that the case studies do not directly relate to, recommendations for them will be generated out of what has been found. In addition to this, certain design principles used by the case studies can be directly applied to these domains.

\section{Findings}
\subsection{Helpful Instructional Theories}
\subsection{Case Studies and the Similarities in Design Principles}
